---
title: "Jan 2019 Testosterone Statistics"
author: "Sophia S. Carryl"
date: "1/15/2019"
output:
  html_document:
    df_print: kable
    highlight: haddock
    number_sections: yes
    toc: yes
  word_document:
    toc: no
  pdf_document:
    df_print: kable
    highlight: haddock
    number_section: yes
    toc: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,tidy.opts=list(length.cutoff=40),tidy=TRUE)
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
library("ggpubr")
library("ggpmisc")
library("smatr")
library("dplyr")
library("ggplot2")
library("dunn.test")
library("RColorBrewer")
library("multcomp")
library("FSA")
library("lmerTest")
library("lme4")
library("nlme")
library("sjPlot")
library("sjmisc")
library("car")
library("visreg")
library("plyr")
library("tidyr")
library("lsmeans")
library("agricolae")
library("lubridate")
library("scales")
library("ggrepel")

```


#Standard Error
```{r}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}
```


# Testosterone 

```{r}
Testosterone = read.csv("/Volumes/SophCarr/HouseSparrows/Testosterone/TestosteroneHormones_Dec2018.csv")

Testosterone = subset(Testosterone, select = c("BirdID", "Sex", "BreedingStatus", "Season", "Tail", "Wing",  "Tarsus", "Beak", "Weight", "Month", "Location", "Testosterone.ng.g.", "Corticosterone.ng.g.", "Gradient", "Age", "Date", "Astro_Season", "CCPlate_Number", "Tplate_Number"))

colnames(Testosterone) = c("BirdID", "Sex", "BreedingStatus", "Season", "Tail", "Wing", "Tarsus", "Beak", "Mass", "Month", "Location", "Testo", "CC", "Gradient", "Age", "Date","Astro_Season","CCPlate_Number", "TPlate_Number")

Testosterone$CCPlate_Number = as.character(Testosterone$CCPlate_Number)
Testosterone$TPlate_Number = as.character(Testosterone$TPlate_Number)


Testosterone$LogT = log(Testosterone$Testo)
Testosterone$LogCC = log(Testosterone$CC)
Testosterone = subset(Testosterone, Age != "Nestling")
# Testosterone = subset(Testosterone, Location != "Lansing")
# Testosterone = subset(Testosterone, Age != "U")
# Testosterone = Testosterone %>% filter(!is.na(LogT))


Testosterone$Date = as.Date(Testosterone$Date, format = '%m/%d/%y')
Testosterone$Month = factor(Testosterone$Month , levels = c("April", "May", "June", "July", "August","September", "October","November", "December"))
Testosterone$Season = factor(Testosterone$Season , levels = c("Spring", "Summer", "Fall", "Winter"))
Testosterone$Astro_Season = factor(Testosterone$Astro_Season , levels = c("Spring", "Summer", "Fall", "Winter"))
Testosterone$Age = factor(Testosterone$Age , levels = c("Juvenile", "Adult"))
Testosterone$Gradient = factor(Testosterone$Gradient, levels = c("Urban", "Suburban", "Rural"))

Testosterone$Month_Date = format(as.Date(Testosterone$Date), "%m-%d")
Testosterone$Month_Date = as.Date(paste0(Testosterone$Month_Date, "-2000"),format = '%m-%d-%y' )
```


```{r}
#Testosterone = Testosterone %>% filter(!is.na(Month))
Nesting_group = c("April", "May", "June", "July", "August")
Molting_group = c("September", "October")
Wintering_group = c("November","December")

Testosterone$Status = with(Testosterone, ifelse(Month %in% Nesting_group, "Nesting", 
                          ifelse(Month %in% Molting_group, "Molting", "Wintering")))

Testosterone$Status = factor(Testosterone$Status, levels = c("Nesting", "Molting", "Wintering"))
```


```{r}
count(Testosterone, c("Status"))

```

```{r}
count(Testosterone, c("Age"))
```


```{r}
#Testosterone = subset(Testosterone, BirdID != "LPZ382" & BirdID != "LPZ330")
A_Testosterone = subset(Testosterone, Age == "Adult")
J_Testosterone = subset(Testosterone, Age == "Juvenile")
U_Testosterone = subset(Testosterone, Sex != "U")

```

```{r}
Summarize(LogCC ~ Sex,
          data=A_Testosterone,
          digits=3)
```

```{r}
ggplot(Testosterone, aes(x = Status, y = LogT, fill = Status)) +
  theme_bw() +
  stat_summary(fun.y = mean, geom = "bar",position=position_dodge()) +
  stat_summary(fun.data = mean_se, fun.args = list(mult = 1), geom = "errorbar", width = 0.2,position=position_dodge(.9)) +
  scale_fill_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
    # theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Log Testosterone (ng/g)", x = "Date", title = "Meteorological Seasons",
  caption = "Meteorological seasons begin on the first day of the months that include the equinoxes and solstices.") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(vjust = -1, hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
    theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15))
```

```{r}
ggplot(A_Testosterone, aes(x = Astro_Season, y = LogT, fill = Astro_Season)) +
  theme_bw() +
  stat_summary(fun.y = mean, geom = "bar",position=position_dodge()) +
  stat_summary(fun.data = mean_se, fun.args = list(mult = 1), geom = "errorbar", width = 0.2,position=position_dodge(.9)) +
  scale_fill_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
    # theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Log Testosterone (ng/g)", x = "Date", title = "Astronimical Seasons",
  caption = "Astronomical seasons use the dates of equinoxes and solstices to mark the beginning and end\nof the seasons.") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(vjust = -1, hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
    theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15))
```

##Sex
```{r}
ggplot(A_Testosterone, aes(x = Sex, y = LogT, fill = Sex)) +
  theme_bw() +
  stat_summary(fun.y = mean, geom = "bar",position=position_dodge()) +
  stat_summary(fun.data = mean_se, fun.args = list(mult = 1), geom = "errorbar", width = 0.2,position=position_dodge(.9)) +
  scale_fill_manual(values = c("thistle","hotpink3"), 
                     name=" ") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Log (ng/g)", x = " ", title = " ",
  caption = "") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(vjust = -1, hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
    theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15))
```

##Age
```{r}
ggplot(Testosterone, aes(x = Month, y = LogT, fill = Age)) +
  #facet_wrap(.~Sex) +
  theme_bw() +
  stat_summary(fun.y = mean, geom = "bar",position=position_dodge()) +
  stat_summary(fun.data = mean_se, fun.args = list(mult = 1), geom = "errorbar", width = 0.2,position=position_dodge(.9)) +
  #scale_x_discrete(limits =c("Juvenile", "Adult")) +
  scale_fill_manual(values = c("darksalmon", "darkorange3"), 
                     name="Age") +
    theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Testosterone Log (ng/g)", x = " ", title = "",
  caption = "") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(vjust = -1, hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
    theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15))
```


```{r}
ggplot(A_Testosterone, aes(x=Status , y=LogT)) + 
  geom_bar(stat = "identity", aes(fill = Status))
```


###Least Mean Square

```{r}
# model = lm(LogT ~ Age,
#            data = Testosterone)
# 
# 
# lsmeans(model,
#        pairwise ~ Age)
```


```{r}
Testosterone = subset(Testosterone, BirdID != "LPZ382" & BirdID != "LPZ330")
A_Testosterone = subset(Testosterone, Age == "Adult")
J_Testosterone = subset(Testosterone, Age == "Juvenile")
```

###Scatter Plot
 #Astronomical Seasons
```{r}
ggplot(A_Testosterone, aes(x=Month_Date , y=Testo)) + 
  geom_point(size = 9, aes(color = Astro_Season,shape =Sex)) +
  theme_bw() +
  scale_color_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
  scale_x_date(date_breaks = "1 month",labels = date_format("%m-%d")) +
  geom_smooth(method="loess", se=TRUE, fullrange=FALSE, level=.95, color = "antiquewhite4") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Log Testosterone (ng/g)", x = "Date", title = "Astronimical Seasons",
  caption = "Astronomical seasons use the dates of equinoxes and solstices to mark the beginning and end\nof the seasons.") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(vjust = -1, hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
    theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15)) +
  annotate("rect", xmin = as.Date("2020-08-01"), xmax = as.Date("2020-10-01"), ymin = -1.1,               ymax = -1,alpha = .15, fill = "#8c6bb1", color = "grey") +
  annotate("rect", xmin = as.Date("2020-08-01"), xmax = as.Date("2020-09-01") , ymin = -1.1,              ymax = -1,alpha = .5, fill = "#8c6bb1", color = "grey58") +
  annotate("rect", xmin = as.Date("2020-04-01"), xmax = as.Date("2020-09-01"), ymin = -1.4,
           ymax = -1.5,alpha = .3, fill = "#fec44f", color = "grey") +
  annotate("rect", xmin = as.Date("2020-04-01"), xmax = as.Date("2020-08-01"), ymin = -1.4,
           ymax = -1.5, alpha = .4, fill = "#fec44f", color = "grey")

```


# Meteorological Season
```{r}
ggplot(A_Testosterone, aes(x=Month_Date , y=LogT)) + 
  geom_point(size = 9, aes(color = Season, shape = Sex)) +
  theme_bw() +
  scale_color_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
  scale_x_date(date_breaks = "1 month",labels = date_format("%m-%d")) +
  geom_smooth(method="loess", se=TRUE, fullrange=FALSE, level=.95, color = "antiquewhite4") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Log Testosterone (ng/g)", x = "Date", title = "Meteorological  Seasons",
  caption = "Meteorological seasons begin on the first day of the months that include the equinoxes and solstices.") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
        theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15)) +
  annotate("rect", xmin = as.Date("2020-08-01"), xmax = as.Date("2020-10-01"), ymin = -1.1,               ymax = -1,alpha = .15, fill = "#8c6bb1", color = "grey") +
  annotate("rect", xmin = as.Date("2020-08-01"), xmax = as.Date("2020-09-01") , ymin = -1.1,              ymax = -1,alpha = .5, fill = "#8c6bb1", color = "grey58") +
  annotate("rect", xmin = as.Date("2020-04-01"), xmax = as.Date("2020-09-01"), ymin = -1.4,
           ymax = -1.5,alpha = .3, fill = "#fec44f", color = "grey") +
  annotate("rect", xmin = as.Date("2020-04-01"), xmax = as.Date("2020-08-01"), ymin = -1.4,
           ymax = -1.5, alpha = .4, fill = "#fec44f", color = "grey")
  # geom_text(aes(label = BirdID))
```

#
```{r}
# A_Testosterone = A_Testosterone %>% filter(!is.na(LogCC))
# A_Testosterone = A_Testosterone %>% filter(!is.na(LogT))

ggplot(A_Testosterone, aes(x=LogCC , y=LogT)) + 
  geom_point(size = 9, aes(color = Season)) +
  theme_bw() +
  scale_color_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
  #scale_x_date(date_breaks = "1 month",labels = date_format("%m-%d")) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=.95, color = "antiquewhite4") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  labs(y = "Testosterone", x = "Corticosterone", title = "",
  caption = "") +
   theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
         plot.caption = element_text(hjust = -0, size = 10, face = "italic")) +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
        theme(axis.text.x=element_text(size = 15),
    axis.text.y=element_text(size = 15))
  # geom_text(aes(label = BirdID))
  # geom_text(aes(label=ifelse(Age == "Adult" & Season == "Fall",as.character(BirdID),'')),hjust=0,vjust=0)

```

```{r}
M_S = subset(Testosterone, Sex == "M" & Season == "Spring")
```

```{r}
ggplot(A_Testosterone, aes(x=LogCC, y=LogT)) + 
  geom_point(size = 8, aes(color = Astro_Season)) +
  geom_smooth(method=lm, se=TRUE, color = "black") +
  stat_cor(method = "pearson", label.y = 1.3, label.x = 0.058, 
           size = 5) +
  stat_cor(method = "pearson", aes(color = Astro_Season), #label.y = 1.5,
           label.x = 1, size = 6) +
  theme_classic() +
  stat_poly_eq(formula = y ~ x,
               aes(label = paste(..rr.label..)), 
               parse = T, label.x.npc = .09, label.y.npc = .9, 
               size = 5) +
         theme(axis.title.x = element_text(size = 12)) +
         theme(axis.title.y = element_text(size = 12)) +
         theme(axis.text.x=element_text(size = 12),
               axis.text.y=element_text(size = 12)) +
  # scale_x_continuous(breaks = seq(25,40, by = 2)) +
  # scale_y_continuous(breaks = seq(-2,2, by = .5))+
  annotate("text", x = , y = , label = 
          'atop(bold("Caption:"),"")',
          colour = "black", parse = TRUE, size = 5) +
  # ylab("Log-Testosterone Feathers (ng/g)") +
  # xlab(" ") +
  theme(legend.title = element_text(colour="black", size=10, 
        face="bold")) +
  theme(legend.text = element_text(colour="black", size = 10, face = 
        "bold")) +
  theme(legend.background = element_rect(fill="white", size=.5, 
        linetype="dotted")) +
    # scale_color_manual(values=c("darkgreen", "#E69F00", "darkblue"))
  # scale_color_manual(values=c("darkslateblue","lavenderblush4"))
    scale_color_manual(values=c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"))
```


###Subset Data
```{r}
#Testosterone = subset(Testosterone, BirdID != "LPZ306" & BirdID != "HHS211" & BirdID != "HHS85" & BirdID != "HHS77" & BirdID != "LPZ303")

#Testosterone = subset(Testosterone, BirdID != "LPZ382")


# Testosterone = Testosterone %>% filter(!is.na(LogT)) 

#Testosterone = subset(Testosterone, Sex == "")
# Testosterone = subset(Testosterone, Age == "Adult")
```


```{r}
count(Testosterone, c("TPlate_Number"))
```

###Stand Error
```{r}
TestSE <- summarySE(Testosterone, measurevar="LogT", groupvars=c("Date", "Gradient"))
```

```{r}
ggplot(TestSE, aes(x = Date, y = LogT, color = Gradient, group = Gradient)) +
  geom_line(size = 2.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin=LogT-se, ymax=LogT+se), width=.1, size = 2) +
  theme_classic () +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  #scale_x_discrete(limits =c("Fall", "Winter", "Spring", "Summer")) +    
 # scale_x_discrete(limits =c("April", "May", "June", "July", "August","September", "November", "December")) +
  # scale_color_manual(values=c("firebrick4", "darkgreen")) +
  scale_color_manual(values=c("darkslateblue","lavenderblush4","darkgreen")) +
  ylab("Log-Testosterone Feathers (ng/g)") +
  xlab("") +
  theme(axis.title.x = element_text(size = 15)) +
  theme(axis.title.y = element_text(size = 15)) +
  theme(axis.text.x=element_text(size = 15),
        axis.text.y=element_text(size = 15)) +
  scale_y_continuous(breaks = seq(-1,2, by = .25)) +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  annotate("rect", xmin = 0.60, xmax = 11.2, ymin = -1.1, ymax = 1.8,alpha = .15, color = "grey") +
  annotate("rect", xmin = 0.60, xmax = 10.2 , ymin = -1.1, ymax = 1.8,alpha = .5, color = "grey58") +
  # annotate("rect", xmin = 5, xmax = 7, ymin = -2, ymax = -1.5,alpha = .3, fill = "olivedrab", color = "grey") +
  # labs(title = " ") +
  # annotate("rect", xmin = 5.5, xmax = 6.9, ymin = -2, ymax = -1.5,alpha = .4, fill = "olivedrab", color = "grey") +
  labs(title = " ") 
```



```{r}
t.test(LogT ~ Sex, paired = FALSE, alternative = "two.sided",var.equal = TRUE, data = Testosterone)
```

```{r}
ggplot(Testosterone, aes(Date,LogT)) + 
  geom_boxplot(aes(color = Sex)) +
  #scale_x_discrete(limits =c("April", "May", "June", "July", "August","September", "October", "November", "December")) +
  # scale_x_discrete(limits =c("Fall","Winter", "Spring", "Summer")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  #geom_jitter(position=position_jitter(0.0), size = 2) +
  #scale_fill_manual(values=c("firebrick4", "darkgreen")) +
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) +
  theme(axis.text.x = element_text(size = 16, color = "black"),
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"),
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  annotate("rect", xmin = 0.60, xmax = 11.4, ymin = -1.1, ymax = 1.8,alpha = .15, color = "grey") +
  annotate("rect", xmin = 0.60, xmax = 10.2 , ymin = -1.1, ymax = 1.8,alpha = .5, color = "grey58") +
  annotate("rect", xmin = 10, xmax = 14, ymin = -2, ymax = -1.5,alpha = .3, fill = "olivedrab", color = "grey") +
  annotate("rect", xmin = 10.5, xmax = 12.8, ymin = -2, ymax = -1.5,alpha = .4, fill = "olivedrab", color = "grey") +
  labs(title = " ") +
  ylab("Log-Testosterone") +
  xlab(" ")
```


```{r}
ggplot(A_Testosterone, aes(Sex,LogCC)) + 
  geom_boxplot(aes(fill = Season)) +
  facet_grid(.~Location) +
  #scale_x_discrete(limits =c("April", "May", "June", "July", "August","September", "October", "November", "December")) +
  # scale_x_discrete(limits =c("Fall","Winter", "Spring", "Summer")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  #geom_jitter(position=position_jitter(0.0), size = 2) +
  #scale_fill_manual(values=c("firebrick4", "darkgreen")) +
  # scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) +
  # scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) +
  theme(axis.text.x = element_text(size = 16, color = "black"),
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"),
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.text.x = element_text(angle = 45,hjust = 1)) +
  # annotate("rect", xmin = 0.60, xmax = 11.4, ymin = -1.1, ymax = 1.8,alpha = .15, color = "grey") +
  # annotate("rect", xmin = 0.60, xmax = 10.2 , ymin = -1.1, ymax = 1.8,alpha = .5, color = "grey58") +
  # annotate("rect", xmin = 10, xmax = 14, ymin = -2, ymax = -1.5,alpha = .3, fill = "olivedrab", color = "grey") +
  # annotate("rect", xmin = 10.5, xmax = 12.8, ymin = -2, ymax = -1.5,alpha = .4, fill = "olivedrab", color = "grey") +
  labs(title = " ") +
  ylab("Log-Testosterone") +
  xlab(" ")
```

```{r}
res = aov(LogCC ~ Season * Gradient * Sex, data = A_Testosterone)
summary(res)
```



```{r}
Testosterone = read.csv("/Volumes/SophCarr/HouseSparrows/Testosterone/TestosteroneHormones_Dec2018.csv")

Testosterone = subset(Testosterone, select = c("BirdID", "Sex", "BreedingStatus", "Season", "Tail", "Wing",  "Tarsus", "Beak", "Weight", "Month", "Location", "Testosterone.ng.g.", "Corticosterone.ng.g.", "Gradient", "Age", "Date"))
colnames(Testosterone) = c("BirdID", "Sex", "BreedingStatus", "Season", "Tail", "Wing", "Tarsus", "Beak", "Mass", "Month", "Location", "Testo", "CC", "Gradient", "Age", "Date")

Testosterone$LogT = log(Testosterone$Testo)
Testosterone = subset(Testosterone, Location != "Lansing")
Testosterone = subset(Testosterone, Age == "Adult")
```

```{r}
ggplot(Testosterone, aes(x=Sex, y=LogT, fill = Sex)) + 
  geom_boxplot() +
  theme_classic () +
  # scale_x_discrete(limits =c("April", "May", "June", "July", "August", "November")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(),
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  #scale_fill_manual(values=c("firebrick4", "darkgreen")) +
  scale_fill_manual(values=c("darkslateblue","lavenderblush4")) +
  # geom_jitter(position=position_jitter(0.0), size = 2) +
  theme(axis.text.x = element_text(size = 16, color = "black"),
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"),
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  labs(title = " ") +
  ylab("Log Testosterone Feathers (ng/g)") +
  xlab(" ")
```


###Scale Mass Index
```{r, echo=FALSE}
LinearMean = 12.66444	
SMA = 0.6369778

SMI = Testosterone %>%
  mutate(ScaleMassIndex = Mass*(LinearMean/Beak)^SMA) %>%
  filter(!is.na(ScaleMassIndex))
```

###Test Normality 
```{r}
shapiro.test(as.numeric(SMI$LogT)) 
shapiro.test(as.numeric(SMI$ScaleMassIndex)) 
```
**ANS:** Data are not normally distributed for Scale Mass Index.  

###Test Variance
```{r}
leveneTest(LogT ~ Season, data = SMI)
leveneTest(ScaleMassIndex ~ Season, data = SMI)
```
**ANS:** Data do not have equal variance for Log-testosterone

###Equation for Linear Regression
```{r}
my.formula <- y ~ x
```

*** 

###Regression Plot Testosterone by ScaleMassIndex
```{r, fig.width = 7, echo = FALSE}
ggscatter(SMI, x = "LogT", y = "ScaleMassIndex", 
          add = "reg.line", conf.int = T, 
          cor.coef = T, cor.method = "spearman",
          xlab = "Testosterone (ng/g) Feathers", ylab = "Scaled-mass Index") +
  stat_poly_eq(formula = my.formula, 
               aes(label = paste(..rr.label..)), 
               parse = T, label.x.npc = .09, label.y.npc = .9)
```

***
<!-- ###Regression Plot Testosterone by Log Corticosterone -->
<!-- ```{r, fig.width = 7, echo = FALSE} -->
<!-- ggscatter(Testosterone, x = "LogT", y = "LogCC",  -->
<!--           add = "reg.line", conf.int = T,  -->
<!--           cor.coef = T, cor.method = "spearman", -->
<!--           xlab = "Testosterone (ng/g) Feathers", ylab = "Corticosterone (ng/g) Feathers") + -->
<!--   stat_poly_eq(formula = my.formula,  -->
<!--                aes(label = paste(..rr.label..)),  -->
<!--                parse = T, label.x.npc = .09, label.y.npc = .9) -->
<!-- ``` -->

***

#Gradient

###Summary Statistics 
```{r}
Summarize(LogT ~ Gradient,
          data=Testosterone,
          digits=3)
```

###Least Mean Square
```{r}
model = lm(LogCC ~ TPlate_Number,
           data = A_Testosterone)


lsmeans(model,
       pairwise ~ TPlate_Number)
```

###ANOVA
```{r}
A_Testosterone = subset(Testosterone, Age == "Adult")
A_CC_Testosterone = A_Testosterone %>% filter(!is.na(CCPlate_Number))
A_T_Testosterone = A_Testosterone %>% filter(!is.na(TPlate_Number))
```

###Two way ANOVA

```{r}
res = aov(LogCC ~ Season * CCPlate_Number, data = A_CC_Testosterone )
summary(res)

res.aov2 <- aov(LogT ~ Season * TPlate_Number, data = A_T_Testosterone)
summary(res.aov2)
```

###Student-Newman-Keuls Test
```{r}
SNK.test(res, "CCPlate_Number", console = TRUE, group = FALSE)

SNK.test(res.aov2 , "TPlate_Number", console = TRUE, group = FALSE)
```

###Tukey HSD
```{r}
TukeyHSD(res.aov2)
```


###Pairwise T-test
```{r}
pairwise.t.test(A_CC_Testosterone$LogCC, A_CC_Testosterone$CCPlate_Number, 
                p.adjust.method = "fdr")

pairwise.t.test(A_T_Testosterone$LogT, A_T_Testosterone$TPlate_Number, pool.sd = FALSE,
                p.adjust.method = "fdr")
```




###Dunn Test
```{r}
dunnTest(LogT ~ TPlate_Number,
         data=A_T_Testosterone ,
         method="bh")
```

###Box and Whisker: Gradient

```{r, echo = FALSE}
ggplot(A_T_Testosterone, aes(x=TPlate_Number, y=LogT)) + 
  geom_boxplot() +
  theme_classic () +
  # scale_x_discrete(limits =c("Urban", "Suburban", "Rural")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  # scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) +
  geom_jitter(position=position_jitter(0.0), size = 12, aes(color = Location, shape = Season)) +
  theme(axis.text.x = element_text(size = 16, color = "black"), 
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"), 
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+ 
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  labs(title = " ") +
  scale_color_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
  ylab("Log-Testosterone") +
  xlab(" ") +
  guides(fill=FALSE)
```
```{r, echo = FALSE}
ggplot(A_CC_Testosterone, aes(x=CCPlate_Number, y=LogCC)) + 
  geom_boxplot() +
  theme_classic () +
  # scale_x_discrete(limits =c("Urban", "Suburban", "Rural")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  # scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) +
  geom_jitter(position=position_jitter(0.0), size = 12, aes(color = Season)) +
  theme(axis.text.x = element_text(size = 16, color = "black"), 
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"), 
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+ 
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  labs(title = " ") +
  scale_color_manual(values = c("#bae4bc", "#238b45", "#80b1d3", "#1f78b4"), 
                     name="Season") +
  ylab("Log-Corticosterone") +
  xlab(" ") +
  geom_text(aes(label=ifelse(LogCC < -1 , as.character(BirdID),'')),hjust=0,vjust=0)
```

***

#Season
```{r}
count(A_Testosterone, c("Season", "Gradient"))
```

##Urban
```{r}
Testosterone_Urban = subset(Testosterone, Gradient == "Urban")
```

###Least Mean Square
```{r}
model = lm(LogT ~ Season,
           data = Testosterone_Urban)

lsmeans(model,
       pairwise ~ Season)
```

###Student's T-test
```{r}
pairwise.t.test(Testosterone_Urban$LogT, Testosterone_Urban$Season, p.adjust.method = "fdr")
```

###One-Way ANOVA
```{r}
res = aov(LogT ~ Season, data = Testosterone_Urban)
summary(res)
```

###Student-Newman-Keuls Test
```{r}
SNK.test(res, "Season", console = TRUE, group = FALSE)
```

###Tukey HSD
```{r}
TukeyHSD(res)
```

###Dunn Test
```{r}
dunnTest(LogT ~ Month,
         data=Testosterone_Urban,
         method="bh")
```


###Box and Whisker: Urban
```{r, echo = FALSE, fig.width = 9}
ggplot(Testosterone_Urban, aes(x=Season, y=LogT)) + 
  geom_boxplot(color = "black", fill = "gray") +
  theme_classic () +
  #scale_x_discrete(limits =c("April", "May", "June", "July")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  geom_jitter(position=position_jitter(0.0), size = 2) +
  theme(axis.text.x = element_text(size = 16, color = "black"), 
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"), 
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+ 
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  labs(title = " ") +
  ylab("Log-Testosterone") +
  xlab(" ") +
  guides(fill=FALSE)
```

***

##Suburban
```{r}
Testosterone_Suburban = subset(Testosterone, Gradient == "Suburban")
```

###Least Mean Square
```{r}
model = lm(LogT ~ Season,
           data = Testosterone_Suburban)

lsmeans(model,
       pairwise ~ Season)
```

###Student's T-test
```{r}
pairwise.t.test(Testosterone_Suburban$LogT, Testosterone_Suburban$Season, p.adjust.method = "fdr")
```

###One-Way ANOVA
```{r}
res = aov(LogT ~ Season, data = Testosterone_Suburban)
summary(res)
```

###Student-Newman-Keuls Test
```{r}
SNK.test(res, "Season", console = TRUE, group = FALSE)
```

###Tukey HSD
```{r}
TukeyHSD(res)
```

###Dunn Test
```{r}
dunnTest(LogT ~ Month,
         data=Testosterone_Suburban,
         method="bh")
```


###Box and Whisker: Urban
```{r, echo = FALSE, fig.width = 9}
ggplot(Testosterone_Suburban, aes(x=Season, y=LogT)) + 
  geom_boxplot(color = "black", fill = "gray") +
  theme_classic () +
  #scale_x_discrete(limits =c("April", "May", "June", "July")) +
  theme(panel.background = element_blank(), panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black"), legend.key = element_blank(),
        legend.background = ) +
  geom_jitter(position=position_jitter(0.0), size = 2) +
  theme(axis.text.x = element_text(size = 16, color = "black"), 
        axis.title.x = element_text(size = 20, color = "black", face = "bold")) +
  theme(axis.text.y  = element_text(size = 16, color = "black"), 
        axis.title.y = element_text(size = 20, color = "black", face = "bold"))+ 
  theme(axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  labs(title = " ") +
  ylab("Log-Testosterone") +
  xlab(" ") +
  guides(fill=FALSE)
```

***

#Linear Mix Model

```{r}
# Model1 = lmer(LogT ~ LogCC + (1|Gradient), data = Testosterone, REML = FALSE)
# 
# Model2 = lmer(LogT ~ LogCC*Season + (1|Gradient), data = Testosterone, REML = FALSE)
# 
# anova(Model1,Model2)
```



